Follow-up Samples

### 2017-01-18 submission/manuscript_outline_20161024.Rmd
streamline -Introduction

In this study we investigated what happened to the bacterial microbiome before and after surgery for indivdiuals with either adenoma and carcinoma.  Our anlaysis includes both alpha and beta diversity analysis along with investigation of individual operational taxonomic units (OTUs).  We also utilized Random Forest models and observed how these models as well as specific OTUs within this model performed on before (initial) and after (follow up) surgery samples.  We used these models to look for similar important OTUs to identify the crucial OTUs for not only classifying initial and follow up samples but also lesion or normal.

>>>>

In this study we investigated what happened to the bacterial microbiome before and after surgery for indivdiuals with either adenoma or carcinoma.  Our anlaysis includes both alpha and beta diversity analysis along with investigation of individual operational taxonomic units (OTUs).  We also utilized Random Forest models and observed how these models as well as specific OTUs within them performed before (initial) and after (follow up) surgery.  We also used these models to look for similar important OTUs to identify the crucial OTUs for not only classifying initial and follow up samples but also lesion or normal.
